\section{\textbf{Patents and Publications} \hfill \textcolor{darkblue}{\scriptsize C=Conference, J=Journal, P=Patent, S=In Submission, T=Thesis}}
\vspace{0.2mm}
\small{
\begin{enumerate}[leftmargin=*, labelsep=0.5em, align=left, widest={[\textbf{C.4}]}, itemindent=0em, label={\textbf{[C.\arabic*]}}]
\item Ramlan, S. A., Rashid, A. N. A., Harron, N. A., Saod, A. H. M., Ismail, N., \& Muttalib, A. A. A. (2015). \textbf{API-LESS AUTOMATION: AN IMPLEMENTATION OF A MAJOR ONLINE BANKING FINANCIAL SUMMARY GENERATION}. In \textit{Penang Invention, Innovation and Design 2015}, pp. 1-3. UiTM Cawangan Pulau Pinang. ISBN: 978-967-0841-09-0.

\item Abd Rashid, A. N., Ramlan, S. A., Harron, N. A., Mohd Saod, A. H., Ismail, N., \& Abdul Mutallib, A. A. (2017). \textbf{LogTrack: Development of Logistic Based System for Merong Freight Sdn. Bhd.} In \textit{Creative Innovation without Boundaries (Series 2)}, pp. 13-16. MNNF Publisher. ISBN: 978-967-15509-0-8.

\item Ramlan, S. A., Rashid, A. N. A., Fauzi, N. M., Isa, S. S. M., Harron, N. A., Saod, A. H. M., \& Muttalib, A. A. A. (2017). \textbf{Web-Based Monitoring System for Industrial Training Placement}. In \textit{Creative Innovation without Boundaries (Series 2)}, pp. 47-52. MNNF Publisher. ISBN: 978-967-15509-0-8.

\item Ramlan, S. A., Rashid, A. N. A., Saod, A. H. M., Harron, N. A., \& Muttalib, A. A. A. (2018). \textbf{Web-based Industrial Training Management System}. In \textit{Innovation for Sustainable Growth (Series 1)}, pp. 24-26. MNNF Publisher. ISBN: 978-967-15509-2-2.

\item Ramlan, S. A., Rashid, A. N. A., Elias, M. A. S., Muttalib, A. A. A., Ibrahim, I. R., Ali, F. Z., Harron, N. A., \& Saod, A. H. M. (2019). \textbf{Real-Time Internship Log Reporting using MQTT over Websocket Protocol}. In \textit{Leading Towards Creativity \& Innovation (Series 1)}, pp. 7-10. MNNF Publisher. ISBN: 978-967-15509-8-4.

\item Abdul Aziz, Yiyang, Sunny, Tai Kuan, Noor Aisyah, Chin Keat, et al. (2022). \textbf{TUNANGA – Functional Validation (FV) test content improvement using AI (Tuna) and validation automation framework (NGA)}. \textit{Design \& Test Technology Conference (DTTC)}.
\end{enumerate}
}
